\mytitle

### 2016-11-23 pdocs/thesis/article-introduction.tex
work on Aki's comments

Plasticity can be  accounted in gaming solutions by destructing various bodies based on collision
or impulse exceeding predefined limit.
Nevertheless, breaking of steel or reinforced concrete structures using this approach 
is not appropriate if the simulation is to look realistic. Theory for handling of plasticity 
has been presented already in \cite{cg1988}. 
\cite{Jones:2016:EPD} provides extensive listing of related work during past decades.
\cite{Obrien:2002:GMA} extends previously introduced finite element based method \cite{Obrien:1999:GMA}
to ductile materials.
\cite{muller2005meshless} 
present a method for modeling and animating of elastic and plastic bodies in real time using 
point based animation. This approach has not been widely used in computer games.  
One major issue is collision handling of deformable bodies.
Recently there has been multiple studies which have same target of bringing plasticity 
into wider usage.
\cite{Jones:2016:EPD} introduces an plasticity model which
maps impulses computed by rigid body solved to local example-based deformations.
\cite{Patkar:2015:EDB} presents a method for denting and bending of rigid bodies

\cite{Budsberg:2014:EPD}
Suggested methods are best suited for film production and high end games.

@@

The approach presented in this work can be used in the gaming industry to provide more realistic 
simulations without significant extra work. For gaming purposes, the presented method works 
best in scenarios where the connected parts are heavy. This allows a normal 
integration timestep to be used without stability issues. 
This methodological approach enbles established structural analysis
methods to be combined with modern simulation frameworks.

>>>>

Plasticity can be  accounted in gaming solutions by destructing various bodies based on collision
or impulse exceeding predefined limit.
Nevertheless, breaking of steel or reinforced concrete structures using this approach 
is not appropriate if the simulation is to look realistic. Theory for handling of plasticity 
has been presented already in \cite{cg1988}. 
\cite{Jones:2016:EPD} provides extensive listing of related work during past decades.
\cite{Obrien:2002:GMA} extends previously introduced finite element based method \cite{Obrien:1999:GMA}
to ductile materials.
\cite{muller2005meshless} 
present a method for modeling and animating of elastic and plastic bodies in real time using 
point based animation. This approach has not been widely used in computer games.  
One major issue is collision handling of deformable bodies.
Recently there has been multiple studies which have same target of bringing plasticity 
into wider usage.
\cite{Jones:2016:EPD} introduces an plasticity model which
maps impulses computed by rigid body solved to local example-based deformations.
\cite{Patkar:2015:EDB} presents methods for denting and bending of rigid bodies.
Denting is simulated by creating surface on the target body based on the projectile body
and bending is modelled by augmenting each rigid body with an articulated skeleton.
\cite{Budsberg:2014:EPD} presents a method of simulating flexible materials so
that rigid body fragments are connected by ball and socket joints and plasticity is
modelled by updating constraint parameters after elastic limit has been passed.

@@

The approach presented in this work can be used in the gaming industry to provide more realistic 
simulations. For gaming purposes, the presented method works 
best in scenarios where the connected parts are heavy as this allows a normal 
integration timestep to be used without stability issues. 
This methodological approach enbles established structural analysis
methods to be combined with modern simulation frameworks.

### 2016-11-23 pdocs/thesis/article-section-2.tex
work on Aki's comments

The symbols used in Equations \ref{eq:eomL} and \ref{eq:eomV}
are summarized in Table \ref{tab:eom}.
Figure \ref{fig:eom-contact} describes the collision of two bodies, $B_1$ and $B_2$
where $\vec{r}_i$ is orientation of body $i$,
$\vec{p}_k $ is orientation of contact point $k$,
$\vec{r}_{ik} $ is a vector  between the center of gravity of body $i$ and contact point $k$, 
and
$\vec{n}_{k}$ is the contact normal for contact point $k$.

\begin{figure}[tb!]
\centering
\begin{tikzpicture}
\coordinate (O1) at(2,1);
\coordinate (O2) at(2,4);
\coordinate (C) at(2,2);
\draw (0,0) -- (4,0) -- (4,2) -- (0,2) --(0,0);
\draw (2,2) -- (3.5,5) -- (0.5,5) -- (2,2) ;
\node at (3.5,0.4) {$B_1$};
\filldraw (O1) circle (0.5mm) node[anchor=north] {$\vec{r}_1$};
\node at (2.8,4.5) {$B_2$};
\filldraw (O2) circle (0.5mm) node[anchor=south] {$\vec{r}_2$};
\filldraw (C) circle (0.5mm) node[anchor=north west] {$\vec{p}_1$};
\draw[-{Stealth[length=3mm]}] (O1) -- (C) node[anchor=north east] {$\vec{r}_{11}$};
\draw[-{Stealth[length=3mm]}] (O2) -- (C) node[anchor=south east] {$\vec{r}_{21}$};
\draw[-latex,thick] (C) -- ++(0,1.4) node[anchor=west] {$\vec{n}_{1}$};
\node[anchor=west] at (4.5,4.5) {
$\vec{r}_i$  =  orientation of body $i$
};
\node[anchor=west] at (4.5,4) {$\vec{p}_k $ = orientation of contact point $k$};
\node[anchor=west] at (4.5,3.5) {$\vec{r}_{ik} $ = $\vec{p}_k - \vec{r}_i $};
\node[anchor=west] at (4.5,3) {$\vec{n}_{k} $ = normal for contact point $k$};
\end{tikzpicture}
\caption{Illustration of nomenclature for equations of motion for collision.}
\label{fig:eom-contact}
\end{figure}

@@

Friction in contacts and joint constraints can be handled in a unified way by refactoring
equation \ref{eq:eomV} as,  
\cite{erleben.thesis}
%\citet[p.~66-67]{erleben.thesis}
\begin{equation} \label{eq:eomV2}
\vec{u}^{\, t+\Delta t} = \vec{u}^{\, t}+\Delta t M^{-1}(
 J_{contact}^T \vec{\lambda}_{contact}
+ J_{joint}^T \vec{\lambda}_{joint}
+ \vec{f}_{ext}),
\end{equation}
where Jacobian terms $J_{joint}^T$ for joints are 
derived by taking time derivatives of the kinematic constraints.
Symbols used in Equation \ref{eq:eomV2} are summarized in Table
\ref{tab:eom-g} and Figure \ref{fig:eom-joint},
where $\vec{r}_{anc}^{\,i}$ is used to define at which point
joint constraint is applied.

\begin{figure}
\centering
\begin{tikzpicture}
\coordinate (O1) at(1,1);
\coordinate (O2) at(1,3);
\coordinate (C) at(1,2);
\draw (0,0) -- (2,0) -- (2,2) -- (0,2) --(0,0);
\draw (0,2) -- (2,2) -- (2,4) -- (0,4) --(0,2) ;
\node at (0.5,0.4) {$B_1$};
\filldraw (O1) circle (0.5mm) node[anchor=north] {$\vec{r}_1$};
\node at (0.5,3.5) {$B_2$};
\filldraw (O2) circle (0.5mm) node[anchor=south] {$\vec{r}_2$};
\draw[-{Stealth[length=3mm]}] (O1) -- (C) node[anchor=north east] {$\vec{r}_{anc}^{\,1}$};
\draw[-{Stealth[length=3mm]}] (O2) -- (C) node[anchor=south east] {$\vec{r}_{anc}^{\,2}$};
\node[anchor=west] at (4.5,3.5) {
$\vec{r}_i$  =  orientation of body $i$ 
};
\node[anchor=west] at (4.5,3) {$\vec{r}_{anc}^{\,i} $ = body frame vector $i$};
\end{tikzpicture}
\caption{Illustration of nomenclature for equations of motion for joint.}
\label{fig:eom-joint}
\end{figure}

>>>>

The symbols used in Equations \ref{eq:eomL} and \ref{eq:eomV}
are summarized in Table \ref{tab:eom}.
Figure \ref{fig:eom-contact} describes the collision of two
bodies, rectangular body $B_1$ and triangular body $B_2$
where $\vec{r}_i$ is position of body $i$,
$\vec{p}_k $ is position of contact point $k$,
$\vec{r}_{ik} $ is a vector between the center of gravity of body $i$ and contact point $k$, 
and
$\vec{n}_{k}$ is the contact normal for contact point $k$.
It is common convention that the contact normal points
from the body with the smallest index to the body with the largest index, \cite{erleben.thesis}.
In case of point or edge contacts, averaging the normals of neighboring polygons can be used, \cite{Hahn:1998}.

\begin{figure}[tb!]
\centering
\begin{tikzpicture}
\coordinate (O1) at(2,1);
\coordinate (O2) at(2,4);
\coordinate (C) at(2,2);
\draw (0,0) -- (4,0) -- (4,2) -- (0,2) --(0,0);
\draw (2,2) -- (3.5,5) -- (0.5,5) -- (2,2) ;
\node at (3.5,0.4) {$B_1$};
\filldraw (O1) circle (0.5mm) node[anchor=north] {$\vec{r}_1$};
\node at (2.8,4.5) {$B_2$};
\filldraw (O2) circle (0.5mm) node[anchor=south] {$\vec{r}_2$};
\filldraw (C) circle (0.5mm) node[anchor=north west] {$\vec{p}_1$};
\draw[-{Stealth[length=3mm]}] (O1) -- (C) node[anchor=north east] {$\vec{r}_{11}$};
\draw[-{Stealth[length=3mm]}] (O2) -- (C) node[anchor=south east] {$\vec{r}_{21}$};
\draw[-latex,thick] (C) -- ++(0,1.4) node[anchor=west] {$\vec{n}_{1}$};
\node[anchor=west] at (4.5,4.5) {
$\vec{r}_i$  =  position of body $i$
};
\node[anchor=west] at (4.5,4) {$\vec{p}_k $ = position of contact point $k$};
\node[anchor=west] at (4.5,3.5) {$\vec{r}_{ik} $ = $\vec{p}_k - \vec{r}_i $};
\node[anchor=west] at (4.5,3) {$\vec{n}_{k} $ = normal for contact point $k$};
\end{tikzpicture}
\caption{Illustration of nomenclature for equations of motion for collision.}
\label{fig:eom-contact}
\end{figure}

@@

Friction in contacts and joint constraints can be handled in a unified way by refactoring
equation \ref{eq:eomV} as,  
\cite{erleben.thesis}
%\citet[p.~66-67]{erleben.thesis}
\begin{equation} \label{eq:eomV2}
\vec{u}^{\, t+\Delta t} = \vec{u}^{\, t}+\Delta t M^{-1}(
 J_{contact}^T \vec{\lambda}_{contact}
+ J_{joint}^T \vec{\lambda}_{joint}
+ \vec{f}_{ext}),
\end{equation}
where Jacobian terms $J_{joint}^T$ for joints are 
derived by taking time derivatives of the kinematic constraints.
Symbols used in Equation \ref{eq:eomV2} are summarized in Table
\ref{tab:eom-g} and Figure \ref{fig:eom-joint},
where $\vec{r}_{anc}^{\,i}$ is used to define at which point
joint constraint is applied relative to body $i$.

\begin{figure}
\centering
\begin{tikzpicture}
\coordinate (O1) at(1,1);
\coordinate (O2) at(1,3);
\coordinate (C) at(1,2);
\draw (0,0) -- (2,0) -- (2,2) -- (0,2) --(0,0);
\draw (0,2) -- (2,2) -- (2,4) -- (0,4) --(0,2) ;
\node at (0.5,0.4) {$B_1$};
\filldraw (O1) circle (0.5mm) node[anchor=north] {$\vec{r}_1$};
\node at (0.5,3.5) {$B_2$};
\filldraw (O2) circle (0.5mm) node[anchor=south] {$\vec{r}_2$};
\draw[-{Stealth[length=3mm]}] (O1) -- (C) node[anchor=north east] {$\vec{r}_{anc}^{\,1}$};
\draw[-{Stealth[length=3mm]}] (O2) -- (C) node[anchor=south east] {$\vec{r}_{anc}^{\,2}$};
\node[anchor=west] at (4.5,3.5) {
$\vec{r}_i$  =  position of body $i$ 
};
\node[anchor=west] at (4.5,3) {$\vec{r}_{anc}^{\,i} $ = body frame vector $i$};
\end{tikzpicture}
\caption{Illustration of nomenclature for equations of motion for joint.}
\label{fig:eom-joint}
\end{figure}
